biological data preperation

### 2018-09-05 src/biological_data_prep.Rmd
Solve missinginstitution issue

Now look at the missing institution. Use resname to see if it helps...
```{r}
missinginst <- subset(tidydata, institutioncode == "")
missinginst
```
ok now check for unique resname...
```{r}
missinginst$resname <- as.character(missinginst$resname)
missinginstunique <- unique(tidydata$resname) #makes a variable of institutions
missinginstuniquedordered <- sort(missinginstunique) #just puts the list in 
missinginstuniquedordered <- as.character(missinginstuniquedordered)
missinginstuniquedordered
```
Ugh ok there are quite a few here....

Ok soo looking at the OBIS metadata [e.g.](http://www.iobis.org/explore/#/dataset/2327), this is what they should be

Arctic Species Trend Index (ASTI) : Marine == CAFF
Atlantic Reference Centre Museum of Canadian Atlantic Organisms - Invertebrates and Fishes Data == ARC
Atlantic Zone Monitoring Program Maritimes Region (AZMP) plankton datasets. In: Fisheries and Oceans Canada - BioChem archive == DFOMTMS
BioChem zooplankton samples from the Gully, 2006-2007 == DFOMTMS
BioChem:  Zooplankton of St. Margarets Bay 1968 to 1971. == DFOMTMS
BioChem: DFO Atlantic Zone Monitoring Program plankton datasets - Newfoundland and Labrador Region (OBIS Canada) ==  DFONL
BioChem: Fish, Eggs and Larvae in the Gulf of St. Lawrence == DFOQC
BioChem: Sameoto zooplankton collection == DFOMTMS 
DFO Central and Arctic Multi-species Stock Assessment Surveys == DFOCENARC
DFO Gulf Region Groundfish Research Vessel Surveys == DFOGulf
DFO Maritimes Research Vessel Trawl Surveys Fish Observations == DFOMTMS
DFO Newfoundland and Labrador Region Ecosystem Trawl Surveys == DFOQC
DFO Quebec Region MLI museum == DFOQC
DFO Quebec Region Multispecies bottom trawl surveys == DFOQC
ECNASAP - East Coast North America Strategic Assessment == DFOMTMS
Electronic Atlas of Ichthyoplankton on the Scotian Shelf of North America == DFOMTMS
Fish specimens == ROM
ICES contaminants and biological effects == ICES
Ichthyology Collection - Royal Ontario Museum == ROM
IMR Macroplankton surveys == IMR
Maine Department of Marine Resources Inshore Trawl Survey 2000–2009 == MaineDMR
NAFO/ICNAF - Environmental Surveys - NORWESTLANT 1-3, 1963: Fish eggs and larvae == NAFO
NMNH Vertebrate Zoology Fishes Collections == NMNH
Northeast Fisheries Science Center Bottom Trawl Survey Data == NEFSC
Northern Gulf of St. Lawrence Fishes == DFOMTMS

ok so now you want to fill in the missing institutioncode with the correct data...

maybe just populate the missing values with the same text as resname
...
if institutioncode == ""
institutioncode == "resname"
```{r}
for i in (1:nrow)
```

>>>>

Now look at the missing institution. Use resname to see if it helps...
```{r}
missinginst <- subset(tidydata, institutioncode == "")
missinginst
```
ok now check for unique resname...
```{r}
missinginst$resname <- as.character(missinginst$resname)
missinginstunique <- unique(missinginst$resname) #makes a variable of institutions
missinginstuniquedordered <- sort(missinginstunique) #just puts the list in 
missinginstuniquedordered <- as.character(missinginstuniquedordered)
missinginstuniquedordered
```

Ok soo looking at the [OBIS metadata](http://www.iobis.org/explore/#/dataset/4356), the institution is the Conservation of Arctic Flora and Fauna (CAFF)
```{r}
tidydata$institutioncode <- replace(tidydata$institutioncode, tidydata$institutioncode == "", "CAFF")
whosampled <- unique(tidydata$institutioncode) #makes a variable of institutions
whosampledordered <- sort(whosampled) #just puts the list in 
whosampledordered
```
